Speed and strength of an epidemic intervention

### 2020-01-21 doc/speedstrength.tex
minor tweaks to the figure

\begin{figure}[!th]
\includegraphics[width=\textwidth]{../figure/HIV.pdf}
\caption{
\textbf{The infection kernel of the HIV.}
A. The infection kernel of the HIV is approximated using a sum of two gamma distributions. We assume that the baseline proportion of early transmission is 23\% \citep{hayes2006amplified}.
B. Time series of HIV prevalence in pregnant women in South Africa, 1990 - 2010 \citep{barron2013eliminating}. The initial exponential growth rate of the HIV is estimated by fitting a straight line to log-prevalence (1990 - 1997) by minimizing the sum of squares.
C. Increase in the estimate of the amount of early transmission reduces the estimate of the reproductive number.
Black circle indicates the baseline scenario.
}
\figlab{example}
\end{figure}

@@

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/condom.pdf}
\caption{
\textbf{Understanding condom intervention using strength-based decomposition.}
A. Condom use is thought to reduce probability of transmission by a similar factor throughout the course of infection; thus the proportional reduction $\tsub{L}{condom}$ due to condom use is constant across the course of infection.
B. The estimated amount of early transmission affects estimated strength of the epidemic but not of a condom-based intervention.
}
\figlab{condom}
\end{figure}

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/test_and_treat.pdf}
\caption{
\textbf{Understanding test-and-treat intervention using strength- and speed-based decomposition.}
\swp{We should just say exponentially. I see where you're coming from but the super-exponentiality seems negligible. Plotting on a log scale shows that it's approximately linear.}
A. The effectiveness of test-and-treat intervention is assumed to increase super-exponentially at first, and then saturate. The dashed line shows the corresponding effective strength of the intervention (from \eqref{strengthMean}) assuming 23\% early transmission.
B. Increase in the estimated amount of early transmission decreases the estimated strength of an epidemic as well as the estimated strength of test-and-treat intervention.
C. The hazard rate correesponding to the strength curve in (A). 
The dashed line shows the corresponding effective speed of the intervention (from \eqref{speedMean}) assuming 23\% early transmission.
D. The estimated amount of early transmission does not affect the observed speed of an epidemic but affects the estimated speed of intervention.
Black and red circles indicates the baseline scenarios.
Test-and-treat intervention is modeled phenomenologically: $\tsub{L}{test}(\tau) = \exp\left(\int_0^\tau \tsub{h}{test}(\sigma) d\sigma \right)$ and $\tsub{h}{test}(\tau) = \tsub{h}{max} (1 - \exp(- K f(\tau)))$, where $f(\tau)$ is a gamma probability density function with a mean of $1$ year and a shape parameter of 2, $K = 4/\max(f(\tau))$, and $\tsub{h}{max} = 2\,\mathrm{year}^{-1}$.
}
\figlab{test}
\end{figure}

>>>>

\begin{figure}[!th]
\includegraphics[width=\textwidth]{../figure/HIV.pdf}
\caption{
\textbf{The infection kernel of the HIV.}
(A) The infection kernel of the HIV is approximated using a sum of two gamma distributions. We assume that the baseline proportion of early transmission is 23\% \citep{hayes2006amplified}.
(B) Time series of HIV prevalence in pregnant women in South Africa, 1990 - 2010 \citep{barron2013eliminating}. The initial exponential growth rate of the HIV is estimated by fitting a straight line to log-prevalence (1990 - 1997) by minimizing the sum of squares.
(C) Increase in the estimate of the amount of early transmission reduces the estimate of the reproductive number.
The black circle indicates the baseline scenario.
}
\figlab{example}
\end{figure}

@@

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/condom.pdf}
\caption{
\textbf{Understanding condom intervention using strength-based decomposition.}
(A) Condom use is thought to reduce probability of transmission by a similar factor throughout the course of infection; thus the proportional reduction $\tsub{L}{condom}$ due to condom use is constant across the course of infection.
(B) The estimated amount of early transmission affects estimated strength of the epidemic but not of a condom-based intervention.
The black and red circles indicate the baseline scenario.
}
\figlab{condom}
\end{figure}

\begin{figure}[!t]
\includegraphics[width=\textwidth]{../figure/test_and_treat.pdf}
\caption{
\textbf{Understanding test-and-treat intervention using strength- and speed-based decomposition.}
\swp{We should just say exponentially. I see where you're coming from but the super-exponentiality seems negligible. Plotting on a log scale shows that it's approximately linear.}
(A) The effectiveness of test-and-treat intervention is assumed to increase super-exponentially at first, and then saturate. The dashed line shows the corresponding effective strength of the intervention (from \eqref{strengthMean}) assuming 23\% early transmission.
(B) Increase in the estimated amount of early transmission decreases the estimated strength of an epidemic as well as the estimated strength of test-and-treat intervention.
(C) The hazard rate correesponding to the strength curve in (A). 
The dashed line shows the corresponding effective speed of the intervention (from \eqref{speedMean}) assuming 23\% early transmission.
(D) The estimated amount of early transmission does not affect the observed speed of an epidemic but affects the estimated speed of intervention.
The black and red circles indicate the baseline scenario.
Test-and-treat intervention is modeled phenomenologically: $\tsub{L}{test}(\tau) = \exp\left(\int_0^\tau \tsub{h}{test}(\sigma) d\sigma \right)$ and $\tsub{h}{test}(\tau) = \tsub{h}{max} (1 - \exp(- K f(\tau)))$, where $f(\tau)$ is a gamma probability density function with a mean of $1$ year and a shape parameter of 2, $K = 4/\max(f(\tau))$, and $\tsub{h}{max} = 2\,\mathrm{year}^{-1}$.
}
\figlab{test}
\end{figure}
